Deriving Multi-Headed Projective Dependency Parses \\ from Link Grammar Parses

### 2014-06-03 doc/LinksToDAG.tex

Other researchers may postprocess link grammar parses simply by using the first two columns, which indicate whether a given link label $L$ tended to be oriented rightward or leftward by our ILP.

The labels that do not have a consistent direction are mainly those that connect a conjunction to its conjuncts.\footnote{See \url{http://www.abisource.com/projects/link-grammar/dict/coordination.html}.}  
Our coarsening of the labels (see section~\ref{sec:stability}) discards the characters that distinguish left from right conjuncts.

>>>>

Other researchers could postprocess link grammar parses by using the first two columns.  These indicate whether a given link label $L$ tended to be oriented rightward or leftward by our ILP.

The labels that do not have a consistent direction are mainly those that connect a conjunction to its conjuncts.\footnote{See \url{http://www.abisource.com/projects/link-grammar/dict/coordination.html}.}  
Our coarsening of the labels (see section~\ref{sec:stability}) discarded the characters that distinguish left from right conjuncts.
